### 2024-06-30 multiple-regression.qmd
20240630 - missing packages
20240630 - attempt to fix warning

```{r}

```

@@

library("MOTE")

@@

Using the data, the best fitting regression model is: $y = `{r} regression1_intercept` + `{r} regression1_slope` \cdot x_1$.
In this example, the $R^2$ is $`{r} regression1_rsquare`$.
The equation is not a perfect prediction, but with a single [predictor variable](#sec-correlationalStudy), it captures the majority of the variance in the outcome.

@@

With the second [predictor variable](#sec-correlationalStudy), the best fitting regression model is: $y = `{r} regression2_intercept` + `{r} regression2_slope1` \cdot x_1 + `{r} regression2_slope2` \cdot x_2$.
In this example, the $R^2$ is $`{r} regression2_rsquare`$.
The equation with the second [predictor variable](#sec-correlationalStudy) provides a perfect prediction of the outcome.

>>>>

```{r}
library("petersenlab")
library("tidyverse")
library("knitr")
```

@@

@@

Using the data, the best fitting regression model is: $y = \text{`{r} regression1_intercept`} + \text{`{r} regression1_slope`} \cdot x_1$.
In this example, the $R^2$ is $\text{`{r} regression1_rsquare`}$.
The equation is not a perfect prediction, but with a single [predictor variable](#sec-correlationalStudy), it captures the majority of the variance in the outcome.

@@

With the second [predictor variable](#sec-correlationalStudy), the best fitting regression model is: $y = \text{`{r} regression2_intercept`} + \text{`{r} regression2_slope1`} \cdot x_1 + \text{`{r} regression2_slope2`} \cdot x_2$.
In this example, the $R^2$ is $\text{`{r} regression2_rsquare`}$.
The equation with the second [predictor variable](#sec-correlationalStudy) provides a perfect prediction of the outcome.
